---
title: "Monitoring and Evaluation"
author: "chrispine buxtonre ooko"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
keep_md: true
---
# ABSTRACT

Urban informal settlements in Nairobi, Kenya continue to experience persistent food insecurity driven by poverty, unemployment, and recurrent economic shocks. Humanitarian food security programs increasingly integrate community-based real-time feedback mechanisms (RTFMs) to enhance accountability, responsiveness, and program quality. However, empirical evaluation of these mechanisms within urban informal settlement contexts remains limited.

This study monitored and evaluated the implementation and performance of a community-based real-time feedback system integrated into a humanitarian food security program in selected informal settlements of Nairobi, including Kibera, Mathare, Mukuru kwa Njenga, and Korogocho. A descriptive and analytical Monitoring and Evaluation (M&E) design was adopted using simulated (assimilated) quantitative and qualitative data to model real-world humanitarian operations.

The analysis showed that 67.2% of beneficiaries were aware of available feedback mechanisms, with helpdesks, SMS, and hotlines being the most utilized channels. The average feedback response time was four days, with 72.1% of cases resolved within established Service Level Agreements. Thematic analysis revealed that targeting issues, food quality, staff conduct, food quantity, and distribution delays were the most frequently reported concerns.

The study concludes that real-time feedback mechanisms are effective tools for strengthening accountability and learning in urban humanitarian food security programs when adequately managed. However, continued efforts are required to improve beneficiary awareness, resolve outstanding feedback cases, and address recurrent operational challenges. The use of simulated data provides a valid and ethical approach for demonstrating M&E system evaluation in academic and professional contexts.

# EXECUTIVE SUMMARY

Humanitarian food security interventions in Nairobi’s urban informal settlements operate in complex environments characterized by high population density, vulnerability, and limited access to essential services. Accountability to affected populations is therefore critical to program effectiveness and sustainability. This project evaluated the performance of a community-based real-time feedback mechanism embedded within a humanitarian food security program using simulated data.

The evaluation focused on accessibility, utilization, data quality, timeliness, and effectiveness of the feedback system. A simulated sample of 1,000 beneficiaries was analyzed alongside feedback logs and response tracking data. Multiple feedback channels were assessed, including SMS, hotlines, and community helpdesks.

Findings indicate that the feedback mechanism was functional and actively utilized, with 67.2% beneficiary awareness. Feedback was largely addressed in a timely manner, with an average response time of four days and over 70% of cases resolved within agreed timelines. However, targeting concerns and service delivery issues emerged as recurring themes, highlighting areas requiring programmatic attention.

The evaluation recommends strengthening community sensitization, improving follow-up on unresolved cases, enhancing staff training on accountability and conduct, and institutionalizing regular feedback analysis through dashboards. Overall, the project demonstrates that well-managed real-time feedback systems can significantly enhance accountability, learning, and program quality in urban food security interventions.

# INTRODUCTION

# Background of the Study

Kenya continues to face persistent food insecurity, particularly among urban poor populations residing in informal settlements. According to humanitarian assessments, informal settlements in Nairobi such as Kibera, Mathare, Mukuru kwa Njenga, and Korogocho** experience chronic food insecurity driven by poverty, unemployment, high food prices, and recurrent shocks.

Humanitarian food security programs have increasingly integrated community-based real-time feedback mechanisms (RTFMs) to enhance accountability, responsiveness, and program quality. These mechanisms allow beneficiaries to provide immediate feedback through channels such as SMS, toll-free lines, suggestion boxes, and digital surveys.

Despite their adoption, limited empirical evaluation exists on the effectiveness, data quality, and operational challenges of these feedback systems within urban food security programming in Kenya. This study seeks to fill this gap using simulated (assimilated) data to demonstrate a robust Monitoring and Evaluation (M&E) framework.


#  Problem Statement

While real-time feedback mechanisms are promoted as best practice in humanitarian accountability, their effectiveness in urban informal settlements remains uncertain. Challenges such as limited digital literacy, access barriers, delayed response to feedback, and data quality issues may undermine their intended purpose.

Without systematic monitoring and evaluation, humanitarian actors risk implementing feedback systems that are underutilized, poorly managed, or ineffective, thereby weakening accountability to affected populations. This project evaluates the performance of such systems in Nairobi’s informal settlements using simulated data to model real-world humanitarian operations.



# Project Objectives

# General Objective

To monitor and evaluate the implementation and performance of a community based real-time feedback system integrated into humanitarian food security programs in urban informal settlements of Nairobi, Kenya.

# Specific Objectives

1. To assess the accessibility, functionality, and utilization of the real-time community feedback mechanism among targeted beneficiaries.
2. To analyze the quality, completeness, and timeliness of feedback data generated for effective monitoring and reporting.
3. To identify implementation challenges, best practices, and lessons learned in managing real-time feedback mechanisms.


# Research Questions

1. How accessible and functional is the real-time feedback mechanism for beneficiaries in food-insecure urban settlements?
2. What is the quality and timeliness of feedback data generated through the system?
3. What operational challenges and best practices influence effective implementation?



# Significance of the Study

* Supports NGOs and humanitarian agencies in improving accountability systems
* Strengthens MEAL system design and reporting
* Provides a replicable M&E framework using simulated data
* Useful for academic research, internships, and donor reporting

# METHODOLOGY

# Study Design

This study adopted a descriptive and analytical Monitoring and Evaluation (M&E) design. The design focused on assessing the implementation, functionality, and performance of a community-based real-time feedback mechanism (RTFM) integrated into a humanitarian food security program.

The study utilized simulated (assimilated) quantitative and qualitative data to model realistic humanitarian program operations. This approach enabled systematic analysis while avoiding the use of real beneficiary data, in line with ethical and academic requirements.


# Study Area**

The study was contextualized within urban informal settlements in Nairobi, Kenya, characterized by high population density, poverty, and food insecurity. The simulated data reflected conditions in the following settlements:

* Kibera
* Mathare
* Mukuru kwa Njenga
* Korogocho

These areas were selected due to their recurrent inclusion in humanitarian food security interventions.


# Target Population

The target population represented key stakeholders involved in the food security program, including:

* Beneficiaries receiving humanitarian food assistance
* Community mobilizers supporting feedback collection
* MEAL officers responsible for system management
* Program managers overseeing implementation


# Data Sources

The study relied exclusively on simulated data sources, designed to replicate real humanitarian program datasets.

| Data Type            | Description                                     |
| -------------------- | ----------------------------------------------- |
| Beneficiary registry | Simulated demographic and household data        |
| Feedback records     | Simulated SMS, hotline, and in-person feedback  |
| Response logs        | Simulated tracking of actions taken on feedback |
| Staff insights       | Simulated key informant interview summaries     |

No real personal or sensitive information was collected or analyzed.


# Sampling Technique and Sample Size

A simulated sample of 1000 beneficiaries was generated. The sample was stratified by settlement and gender to reflect equitable program coverage.

In addition, purposive sampling was applied to simulate:

* 5 MEAL officers
* 4 community mobilizers
* 3 program managers

This sampling approach aligns with standard humanitarian M&E practice.


# Data Collection Tools

The following simulated data collection tools were used:

* Kobo structured questionnaires
* Feedback categorization matrix
* MEAL response tracking template
* Simulated key informant interview guide

These tools were designed to reflect commonly used NGO MEAL systems.


# Study Variables and Indicators

The study variables were derived from the project objectives and accountability frameworks.

| Variable      | Indicator                                     |
| ------------- | --------------------------------------------- |
| Accessibility | % of beneficiaries aware of feedback channels |
| Utilization   | Feedback submissions per 1,000 beneficiaries  |
| Data Quality  | % of complete feedback records                |
| Timeliness    | Average feedback response time (days)         |
| Effectiveness | % of feedback resolved within SLA             |



# Data Analysis Procedures

Quantitative data are analyzed using descriptive statistics, including frequencies, percentages, and averages. Trend analysis is applied to examine feedback volume over time.

Qualitative feedback is analyzed using thematic analysis, with responses categorized into key themes such as food adequacy, targeting, and staff conduct.

Results are presented using tables, charts, and summary narratives.


# Ethical Considerations

The study adhered to ethical standards relevant to humanitarian research and academic work:

* Exclusive use of simulated (assimilated) data
* No collection of personal identifiers
* Alignment with humanitarian data protection principles
* No risk posed to individuals or communities

Ethical approval was not required due to the non-use of real human subjects.


# Methodological Limitations

* Simulated data may not capture all real-world complexities
* Findings are illustrative rather than generalizable
* Urban population mobility is approximated rather than observed

Despite these limitations, the methodology provides a robust framework for demonstrating effective M&E system evaluation.

# Data Analysis Plan

Data analysis is conducted using both quantitative and qualitative approaches, based on simulated datasets designed to reflect real humanitarian food security program data.

# Quantitative Data Analysis

Quantitative data are analyzed using descriptive statistical techniques. These included:

Frequencies and percentages to summarize beneficiary characteristics, awareness of feedback mechanisms, and utilization of feedback channels.

Measures of central tendency, such as averages, to assess response times and feedback resolution rates.

To examine system performance over time, trend analysis was conducted by aggregating feedback submissions on a monthly basis. This enabled assessment of changes in feedback volume and identification of periods with increased or decreased system utilization.

# Qualitative Data Analysis

Qualitative feedback data are analyzed using thematic analysis. Feedback narratives are reviewed, coded, and grouped into recurrent themes, including food quantity, distribution delays, staff conduct, and targeting concerns.

This approach allowed for systematic identification of key issues raised by beneficiaries and supported interpretation of quantitative findings.

# Data Visualization and Reporting

Findings were presented using visual and tabular formats to enhance interpretation and reporting. These included:

Bar charts and frequency tables to display feedback categories and channel usage.

Trend graphs to illustrate monthly feedback volumes.

Dashboards to summarize key performance indicators such as accessibility, timeliness, and feedback resolution rates.

All visualizations were designed to reflect standard MEAL reporting practices and to support evidence-based decision-making.

# Software and Tools

Data analysis and visualization were conducted using commonly applied tools in humanitarian M&E, including:

Microsoft Excel

R (for statistical analysis and visualization)




Import libraries

```{r}

# Load required libraries:

library(tidyverse)
library(lubridate)
library(janitor)
library(tidyverse)


```


```{r load-data}


## **2. Load the Simulated Dataset**

library(readxl)
Monitoring_and_Evaluation_project_data <- read_excel("C:/Users/Administrator/Desktop/M&E/Monitoring_and_Evaluation_project_data.xlsx")
Monitoring_and_Evaluation_project_data

library(readxl)

# List all sheets in the Excel file
excel_sheets("C:/Users/Administrator/Desktop/M&E/Monitoring_and_Evaluation_project_data.xlsx")

# Import "beneficiaries" sheet
beneficiaries <- read_excel("C:/Users/Administrator/Desktop/M&E/Monitoring_and_Evaluation_project_data.xlsx",
                            sheet = "Beneficiary.xlsx")
beneficiaries

# Import "feedback_txt"
feedback_txt <- read_excel("C:/Users/Administrator/Desktop/M&E/Monitoring_and_Evaluation_project_data.xlsx",
                     sheet = "feedback_txt")
feedback_txt

# Import "Feedback_log"
Feedback_log <- read_excel("C:/Users/Administrator/Desktop/M&E/Monitoring_and_Evaluation_project_data.xlsx",
                     sheet = "Feedback_log")
Feedback_log

# Import "response_tracker"
response_tracker <- read_excel("C:/Users/Administrator/Desktop/M&E/Monitoring_and_Evaluation_project_data.xlsx",
                     sheet = "response_tracker")
response_tracker

head(beneficiaries)


```


```{r}
head(Feedback_log)
```

```{r}
head(response_tracker)
```

Clean column names 
```{r}
beneficiaries <- beneficiaries %>% clean_names()
feedback_txt <- feedback_txt %>% clean_names()
Feedback_log <- Feedback_log %>% clean_names()
response_tracker <- response_tracker %>% clean_names()

```


Descriptive Statistics
Beneficiary Gender Distribution
```{r}
gender_summary <- beneficiaries %>%
  count(gender) %>%
  mutate(percentage = round((n / sum(n))*100,1))

gender_summary

```

Awareness of Feedback Channels
```{r}
awareness_summary <- beneficiaries %>%
  count(awareness_of_feedback) %>%
  mutate(percentage = round((n / sum(n))*100,1))

awareness_summary

```

Merge Feedback and Response Data

```{r}


feedback_data <- Feedback_log %>%
  left_join(response_tracker, by = "feedback_id","feedback_date",)

head(feedback_data)

```

Trend Analysis (Monthly Feedback Volume)
```{r}
colnames(feedback_data)


feedback_data <- feedback_data %>%
  mutate(month = floor_date(feedback_date.x, "month"))

monthly_trend <- feedback_data %>%
  group_by(month) %>%
  summarise(feedback_count = n())

monthly_trend

```
Timeliness Response 
```{r}
colnames(feedback_data)


response_summary <- feedback_data %>%
  summarise(
    average_response_days = round(mean(response_time_days, na.rm = TRUE),1),
    resolved_within_sla = round(mean(response_time_days <= 5, na.rm = TRUE)*100,1)
  )

response_summary

```

Feedback resolution rate
```{r}
resolution_summary <- feedback_data %>%
  count(resolution_status) %>%
  mutate(percentage = round((n / sum(n))*100,1))

resolution_summary

```

Thematic Analysis
```{r}

colnames(feedback_data)

theme_summary <- feedback_data %>%
  count(feedback_category) %>%
  mutate(percentage = round((n / sum(n))*100,1)) %>%
  arrange(desc(n))

theme_summary

```
Visualizations
Feedback Channels
```{r}
# Count number of feedback submissions per channel
channel_summary <- feedback_data %>%
  count(feedback_chanel) %>%                     # counts each channel
  mutate(percentage = round((n / sum(n)) * 100,1)) %>%   # calculate %
  arrange(desc(n))                                # sort descending

# View the summary
channel_summary


ggplot(channel_summary, aes(x = feedback_chanel, y = n)) +
  geom_col(fill="steelblue") +
  labs(title = "Feedback Channel Utilization", x = "Channel", y = "Count") +
  theme_minimal()

```

Monthly Feedback Trend
```{r}
ggplot(monthly_trend, aes(x = month, y = feedback_count)) +
  geom_line(color="darkgreen") +
  geom_point(color="darkgreen") +
  labs(title = "Monthly Feedback Volume", x = "Month", y = "Number of Feedbacks") +
  theme_minimal()

```

```{r}
kpis <- tibble(
  Indicator = c("Awareness of Feedback (%)",
                "Average Response Time (Days)",
                "Feedback Resolved Within SLA (%)"),
  Value = c(
    awareness_summary$percentage[awareness_summary$awareness_of_feedback=="Yes"],
    response_summary$average_response_days,
    response_summary$resolved_within_sla
  )
)

kpis

```

# RESULTS AND FINDINGS

## Interpretation of Data Analysis Results

## Beneficiary Characteristics

The simulated beneficiary dataset consisted of 1,000 beneficiaries drawn from urban informal settlements in Nairobi. Gender distribution was relatively balanced, with 51.4% female and 48.6% male beneficiaries. This near parity suggests that the simulated program achieved gender-balanced coverage, aligning with humanitarian principles of equitable access to assistance .

Such gender balance is important in food security programming, as women often play a central role in household food management and are disproportionately affected by food insecurity in urban informal settlements.



### Awareness of Feedback Mechanisms

Analysis of awareness levels showed that 67.2% of beneficiaries were aware of the available feedback channels, while 32.8% reported no awareness. This indicates a moderate to high level of awareness, suggesting that community sensitization and communication strategies were largely effective.

However, the proportion of beneficiaries who were unaware of the feedback mechanism remains significant. This finding highlights the need for continued community engagement, particularly through community mobilizers and local leaders, to ensure that all beneficiaries are informed about their right to provide feedback and lodge complaints .


### Feedback Volume and System Utilization Trends

Trend analysis of feedback submissions revealed fluctuations over the three-month period analyzed:

* January 2025: 249 feedback cases
* February 2025: 218 feedback cases
* March 2025: 233 feedback cases

The decline in February followed by a slight increase in March suggests that feedback volume is dynamic and context-dependent. Changes in distribution schedules, assistance modalities, or sensitization efforts may influence beneficiary engagement with feedback mechanisms.

Overall, the relatively consistent volume across months indicates steady utilization of the real-time feedback system, reflecting its operational functionality within the simulated humanitarian program .



### Timeliness of Feedback Response

Timeliness analysis showed that the average response time was 4 days, which falls within commonly applied humanitarian Service Level Agreements (SLAs) of 5 days. Furthermore, 72.1% of feedback cases were resolved within the SLA timeframe.

These results indicate that the feedback system demonstrated strong responsiveness, with the majority of beneficiary concerns addressed promptly. Timely responses are critical for building trust, enhancing accountability, and preventing escalation of dissatisfaction among affected populations .


### Feedback Resolution Status

Analysis of resolution outcomes showed that:

* 72.1% of feedback cases were resolved
* 27.9% remained pending

While the majority of cases were successfully resolved, the proportion of pending cases suggests the presence of operational or structural bottlenecks, such as complex targeting issues or coordination delays between program teams. This highlights the importance of continuous follow-up and escalation mechanisms within MEAL systems to ensure closure of outstanding cases.


### Thematic Analysis of Feedback Content

Thematic analysis of feedback categories revealed the following distribution:

* Targeting Issues: 22.0%
* Food Quality: 21.0%
* Staff Conduct: 19.7%
* Food Quantity: 19.6%
* Distribution Delays: 17.7%

Targeting issues emerged as the most common theme, indicating beneficiary concerns regarding inclusion and exclusion errors. Complaints related to food quality and quantity further reflect the sensitivity of beneficiaries to the adequacy and suitability of assistance received.

Reports related to staff conduct underscore the importance of staff behavior, professionalism, and accountability, while distribution delays highlight logistical challenges common in dense urban settings. Overall, the thematic findings provide actionable insights for program improvement .



### Feedback Channel Utilization

Analysis of feedback channels showed diversified use:

* Helpdesk: 35.4%
* SMS: 33.7%
* Hotline: 30.9%

The relatively balanced use of multiple channels suggests that offering multiple access points enhances inclusivity and accommodates different beneficiary preferences and access constraints. The prominence of helpdesks reflects the continued relevance of face-to-face feedback mechanisms, particularly for beneficiaries with limited digital access or literacy.


# Key Performance Indicators (KPIs)

The dashboard-style summary of key indicators showed:

* Awareness of feedback mechanisms: 67.2%
* Average response time: 4 days
* Feedback resolved within SLA: 72.1%

These indicators collectively suggest that the simulated real-time feedback mechanism was functional, responsive, and moderately effective, while also identifying clear areas for strengthening awareness and case closure rates.


# Overall Interpretation

The findings demonstrate that community-based real-time feedback mechanisms can play a critical role in enhancing accountability and program quality in urban humanitarian food security interventions. While system performance was generally strong in terms of responsiveness and utilization, gaps in awareness and unresolved feedback highlight the need for continuous system strengthening, staff capacity building, and community sensitization.



# DISCUSSION OF FINDINGS

## Discussion of Accessibility and Utilization of the Feedback Mechanism

One of the primary objectives of this study was to assess the accessibility, functionality, and utilization of the community-based real-time feedback mechanism among beneficiaries in urban informal settlements of Nairobi.

The findings indicate that 67.2% of beneficiaries were aware of the available feedback channels. This level of awareness suggests that sensitization and communication efforts were largely effective, supporting the functionality of the feedback system. However, the fact that nearly one-third of beneficiaries lacked awareness points to existing gaps in outreach and community engagement.

In terms of utilization, the feedback mechanism demonstrated consistent use across multiple channels, including helpdesks, SMS, and hotlines. The relatively balanced distribution across channels highlights the importance of providing multiple, complementary feedback options to accommodate varying levels of digital access and literacy. These findings align with accountability frameworks that emphasize inclusivity and accessibility in feedback system design.

Research Question Link:
How accessible and functional is the real-time feedback mechanism for beneficiaries?
→ The system is accessible and functional, but awareness gaps remain and require further attention.


## Discussion of Data Quality and Timeliness

The second objective focused on assessing the quality, completeness, and timeliness of feedback data generated by the system.

The analysis showed an average response time of 4 days, with 72.1% of feedback cases resolved within the established Service Level Agreement (SLA). These results indicate strong system responsiveness and effective internal coordination mechanisms. Timely responses are critical for maintaining beneficiary trust and reinforcing accountability to affected populations.

However, the presence of 27.9% unresolved cases suggests operational challenges that may include complex targeting concerns, inter-departmental delays, or limited decision-making authority at field level. While the data quality appears sufficient for monitoring and reporting, strengthening follow-up mechanisms is necessary to ensure full case closure.

Research Question Link:
What is the quality and timeliness of feedback data generated through the system?
→ Feedback data are timely and usable, though unresolved cases indicate areas for system strengthening.


## Discussion of Key Feedback Themes and Operational Challenges

Thematic analysis revealed that targeting issues were the most frequently reported concern, followed by food quality, staff conduct, food quantity, and distribution delays. This pattern suggests that beneficiaries are particularly sensitive to fairness, transparency, and adequacy in food assistance programming.

Complaints related to staff conduct highlight the importance of professional behavior and respectful engagement during service delivery. Similarly, concerns about food quality and quantity underscore the need for consistent supply standards and quality assurance processes.

These findings reflect common challenges documented in humanitarian literature, particularly in densely populated urban informal settlements where resource constraints, high demand, and logistical complexities are prevalent.

Research Question Link:
What operational challenges and best practices influence effective implementation?
→ Key challenges include targeting accuracy, staff conduct, and service delivery efficiency, while best practices include multi-channel feedback access and timely response systems.


## Alignment with Accountability and MEAL Frameworks

Overall, the findings demonstrate that real-time feedback mechanisms can significantly enhance accountability, learning, and program adaptation when adequately resourced and actively managed. The system evaluated in this study aligns with humanitarian Accountability to Affected Populations (AAP) principles by promoting participation, transparency, and responsiveness.

However, continuous improvement is required to address awareness gaps, unresolved cases, and recurrent feedback themes to fully realize the potential of real-time feedback systems.


# CONCLUSIONS AND RECOMMENDATIONS

## Conclusions

Based on the findings of this study, the following conclusions are drawn:

1. Community-based real-time feedback mechanisms are effective tools for enhancing accountability in humanitarian food security programs in urban informal settlements.
2. The feedback system demonstrated functional accessibility and utilization, supported by multiple feedback channels.
3. Feedback data generated were timely and suitable for monitoring and reporting, with most cases resolved within established SLAs.
4. Persistent challenges related to targeting, food quality, staff conduct, and unresolved cases indicate the need for ongoing system strengthening.
5. The use of simulated (assimilated) data provides a valid and ethical approach for demonstrating M&E system evaluation in academic and training contexts.



## Recommendations

Based on the conclusions, the following recommendations are proposed:

### Programmatic Recommendations

1. Strengthen community sensitization to increase awareness of feedback mechanisms, particularly among hard-to-reach beneficiaries.
2. Establish clear escalation pathways for unresolved feedback cases to improve resolution rates.
3. Enhance staff training on accountability, customer care, and professional conduct.
4. Improve targeting verification processes to reduce inclusion and exclusion errors.
5. Maintain and expand multiple feedback channels to promote inclusivity.

### MEAL System Recommendations

1. Integrate automated dashboards to track key performance indicators in real time.
2. Regularly analyze feedback trends to inform adaptive programming.
3. Standardize feedback categorization and documentation tools to improve data quality.
4. Conduct periodic reviews of SLA compliance to strengthen responsiveness.

### Academic and Learning Recommendations

1. Future studies may incorporate real-world data where ethically and legally permissible.
2. Comparative studies between urban and rural settings could provide additional insights.
3. Mixed-method approaches could deepen understanding of beneficiary experiences.



# LOGFRAME (LOGICAL FRAMEWORK)

| Level      | Narrative Summary                                                          | Objectively Verifiable Indicators                      | Means of Verification            | Assumptions                        |
| ---------- | -------------------------------------------------------------------------- | ------------------------------------------------------ | -------------------------------- | ---------------------------------- |
| Impact     | Improved accountability and quality of humanitarian food security programs | % beneficiary satisfaction with program accountability | Beneficiary surveys, evaluations | Stable operating environment       |
| Outcome    | Effective and responsive real-time feedback mechanism                      | % feedback resolved within SLA                         | Response tracking system         | Adequate staffing and coordination |
| Output 1   | Functional feedback system established                                     | Feedback system operational                            | MEAL reports, system logs        | Technology availability            |
| Output 2   | Increased beneficiary awareness                                            | % beneficiaries aware of feedback channels             | Beneficiary surveys              | Effective sensitization            |
| Activities | Sensitization, data collection, response tracking, analysis                | Number of sensitization sessions conducted             | Activity reports                 | Community participation            |

---

# INDICATOR TRACKING TABLE (ITT)

| Indicator                                    | Definition                                                         | Target  | Data Source        | Frequency | Responsible     |
| -------------------------------------------- | ------------------------------------------------------------------ | ------- | ------------------ | --------- | --------------- |
| % beneficiaries aware of feedback mechanisms | Proportion of beneficiaries who know at least one feedback channel | ≥75%    | Beneficiary survey | Quarterly | MEAL Officer    |
| Feedback submissions per 1,000 beneficiaries | Volume of feedback received                                        | ≥50     | Feedback logs      | Monthly   | MEAL Team       |
| Average response time (days)                 | Mean number of days to respond to feedback                         | ≤5 days | Response tracker   | Monthly   | Program Manager |
| % feedback resolved within SLA               | Proportion of feedback cases resolved within agreed timelines      | ≥80%    | Response tracker   | Monthly   | MEAL Officer    |
| % complete feedback records                  | Proportion of feedback records with all required fields            | ≥90%    | Feedback database  | Quarterly | Data Officer    |










